
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
\secretlevel{绝密} \secretyear{2015}

\ctitle{关于先知不等式以及最优停时问题中的截断策略的研究}
% 根据自己的情况选，不用这样复杂
\makeatletter
\ifthu@bachelor\relax\else
  \ifthu@doctor
    \cdegree{理学学士}
  \else
    \ifthu@master
      \cdegree{工学硕士}
    \fi
  \fi
\fi
\makeatother


\cdepartment[计算机]{交叉信息研究院}
\cmajor{计算机科学与技术}
\cauthor{谭子涵}
\csupervisor{王振波副教授}
% 如果没有副指导老师或者联合指导老师，把下面两行相应的删除即可。
% 日期自动生成，如果你要自己写就改这个cdate
%\cdate{\CJKdigits{\the\year}年\CJKnumber{\the\month}月}

\etitle{On the Prophet Inequality and Threshold Strategy in Optimal Stopping Time}
% \edegree{Doctor of Science}
\edegree{Bachelor of Engineering}
\emajor{Computer Science and Technology}
\eauthor{Zihan Tan}
\esupervisor{Professor Zhenbo Wang}
% 这个日期也会自动生成，你要改么？
% \edate{December, 2005}

% 定义中英文摘要和关键字
\begin{cabstract}

最优停时问题是随机优化研究的广泛研究中一个很重要的问题：在一场多轮博弈中，一边获得对于未知或者已知分布的知识，一边又同时需要做出决断选择一个近似最优的策略以优化自己的收益。这类型的问题与在线学习和在线优化等计算机领域科学，运筹学领域研究也有紧密的联系。

本文主要对于随机优化中的最优停时问题做出了理论方面研究与讨论，以先知不等式问题入手，对于一般性分布，讨论了特殊情况下先知的优势比例极限。并且在相应问题中详尽分析了最优停时策略为阶段策略，证明了截断策略的一般性以及成立条件，并且对于不同轮之间的截断值的性质做出了分析。最后，对于随机优化中的特殊分布进行讨论，并分析了在特殊分布之下计算期望收益的算法复杂性与近似性。

\end{cabstract}

\ckeywords{最优停时；截断策略；先知不等式；随机优化}

\begin{eabstract}

The optimal stopping time has been an important problem in stochastic optimization for long. In a multi-stage game, the player is required to learn information from the (known or unknown) latent distribution as well as optimize his utility. Such problem has concrete connection with online learning, a modern topic lying in the intersection between theoretical computer science and operation search.


This thesis mainly focused on the theoretical part of optimal stopping time. Beginning with the setting of prophet inequality problem, we explored the advantage ratio in special cases. Then we studied the pattern of optimal stopping strategy in such type of game and found that threshold strategy can be proved optimal. We then proved some property of threshold values in a threshold strategy. Finally we analyze the computational complexity and approximability of the optimal expected reward with special types of distribution.

\end{eabstract}

\ekeywords{Stopping time; Threshold strategy; Prophet inequality; Stochastic optimization}
